Policing for Profit and the Undermining of Democracy\thanks{The authors thank XX for their feedback and support. All errors are our responsibility.}

### 2021-01-27 markdown/fees_fines_to.Rmd
keep writing

Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities’ alienation from government. American cities’ reliance on fines and fees revenue increased significantly following the 2008 recession—as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services [@Singla2020; @Mughan2020; @Kirk2020; @Martin2018]. Although a body of literature developed over the past decade indicates that criminalization chills political participation, no work has directly investigated the relationship between fines and fees revenue collection and voter turnout. This project intends to fill that gap by testing whether fines and fees at the municipal level influence voter turnout.

@@

Recent work from scholars in sociology and political science, however, indicates that many more voters are also *indirectly* disenfranchised due to over-incarceration and the politically chilling effects of the carceral state. Policing and incarceration shape political socialization: personal contact with police or incarceration is associated with a reduced likelihood of political participation, and that alienating effect extends even to people who have incarcerated family members or who simply reside in affected communities [@Lee2014; @Weaver2010; @Morris2020]. This relationship is complicated, however. In New York City, concentrated stop-and-frisk activity was associated with *reduced* turnout in Congressional elections, but *increased* turnout in the 2008 presidential election as well as the local mayoral election in 2013 [@Laniyonu2019]. It may also be the case that proximal contact differs from personal contact with the criminal legal system—whereas direct experience with criminalization (and incarceration in particular) reduces the likelihood of voting, proximal or indirect experience produces more mixed results. Hannah Walker suggests that police contact that does not lead to a criminal conviction may even mobilize voters—but her survey questions specifically excluded “minor traffic stops,” a primary site of police ticketing [@Walker2014].

@@

Public perceptions of abusive police practices, such as high-profile incidents of police violence or racially discriminatory street stops, can reduce willingness to report crimes or cooperate with law enforcement [@Desmond2016; @Tyler2014). Legitimacy studies have largely focused on police violence or police street stops, but new evidence related to fines and fees has recently emerged. 
In a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government more broadly [@CarpenterII2019].

Although the conceptual framework for police legitimacy has been fruitfully critiqued—Monica @Bell2017 points to legal estrangement and structural exclusion in order to shift the theoretical focus from perceptions of unfairness to substantively unjust practices—the empirical literature on legitimacy is useful to demonstrate how police practices can alienate those subjected to them.  The alienating effect of criminal legal exposure has also been tied to institutional avoidance [see, for instance, @Brayne2014]. .

@@

Figure \ref{fig:marg1} makes clear that higher fees and fines collections lead to lower turnout. The left-hand panel shows the simple bivariate relationship between turnout among registered voters in 2018 and fees and fines collection. The right-hand panel shows the bivariate relationship between the 2018 white-Black turnout gap and fines collections. The turnout gap is calculated by dividing the number of ballots cast by each racial group according to L2 by the estimated 2018 citizen voting age population (CVAP) from the Census Bureau to account for possible registration differences between groups.

```{r, figures-side, fig.show="hold", out.width="50%", echo = FALSE, message = F, warning = F, fig.cap = "\\label{fig:marg1}Dollars per Resident and 2018 Turnout", fig.pos = "H"}
p1 <- readRDS("./temp/simple_scat.rds")
p2 <- readRDS("./temp/simple_scat_gap_bw.rds")
print(p1)
print(p2)
```

Although Figure \ref{fig:marg1} shows that there is a relationship between collections and turnout and the turnout gap, the simple scatter plots cannot demonstrate a causal relationship. To investigate whether there is such a relationship, we employ two-way fixed effect models. In these models, each municipality is observed twice: their first observation includes their (logged + 1) fees and fines per capita from the 2012 COG, their turnout and turnout gap in 2014, and their sociodemographic characteristics from the ACS 5-year estimates from 2012. The second observation includes their (logged + 1) fees and fines from the 2017 COG, their 2018 turnout (gap), and their 2018 5-year ACS demographics. In each case, turnout is measured only among the individuals who were registered in a given municipality in both 2014 and 2018 to control for changes in registration rates, and in Model 2 the turnout gap is calculated using CVAP. Table \ref{tab:tab1} presents the results of these models.

@@

The significant negative association in our analysis provides some support for our first hypothesis: though our preliminary analyses cannot establish causality, they are consistent with a causal story that links fines and fees practices with lower political participation among those who are subjected to them. On the other hand, officials in municipalities with lower turnout may feel more free to rely on fees and fines for revenue collection because they have less fear of electoral repercussions. Our full study will explore these causal relationships directly by supplementing our initial analysis with an analysis of voter turnout and revenue reliance change over time.

That the racial turnout gap is smaller in cities with more fees and fines is surprising, and the opposite of what we expected to find. This could reflect racially disparate policing in cities with low fee collection. It is possible that cities with *low* fees and fines collections disproportionately penalize nonwhite residents; as fees and fines collections increase, however, a larger share of the population --- and, thus, more white voters --- may have a negative interaction with a police officer, thereby *reducing* racial disparities and consequently discrepancies in the racial turnout gap.

Our full study will include a more narrow analysis of turnout in jurisdictions that dramatically increased or decreased ticketing over a comparatively short period of time. For instance, a Florida Times-Union investigation revealed that police in four counties disproportionately issued tickets to Black pedestrians [@Sanders2017]. In Tampa, police issued thousands of tickets to Black cyclists between 2012 and 2015—after journalists reported on the problem, the city began to issue fewer than 100 citations each year as of 2018 [@Zayas2015; @Frago2019]. Systematically conducting such an analysis would likely require collecting and organizing new data, as city-level police ticketing data is inconsistent and not always public information.

\newpage
### Bibliography

>>>>

Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities’ alienation from government. American cities’ reliance on fines and fees revenue increased significantly following the 2008 recession --- as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services [@Singla2020; @Mughan2020; @Kirk2020; @Martin2018]. Although a body of literature developed over the past decade indicates that criminalization chills political participation, no work has directly investigated the relationship between fines and fees revenue collection and voter turnout. This project intends to fill that gap by testing whether fines and fees at the municipal level influence voter turnout.

@@

Recent work from scholars in sociology and political science, however, indicates that many more voters are also *indirectly* disenfranchised due to over-incarceration and the politically chilling effects of the carceral state. Policing and incarceration shape political socialization: personal contact with police or incarceration is associated with a reduced likelihood of political participation, and that alienating effect extends even to people who have incarcerated family members or who simply reside in affected communities [@Lee2014; @Weaver2010; @Morris2020]. This relationship is complicated, however. In New York City, concentrated stop-and-frisk activity was associated with *reduced* turnout in Congressional elections, but *increased* turnout in the 2008 presidential election as well as the local mayoral election in 2013 [@Laniyonu2019]. It may also be the case that proximal contact differs from personal contact with the criminal legal system --- whereas direct experience with criminalization (and incarceration in particular) reduces the likelihood of voting, proximal or indirect experience produces more mixed results. Hannah Walker suggests that police contact that does not lead to a criminal conviction may even mobilize voters --- but her survey questions specifically excluded “minor traffic stops,” a primary site of police ticketing [@Walker2014].

@@

Public perceptions of abusive police practices, such as high-profile incidents of police violence or racially discriminatory street stops, can reduce willingness to report crimes or cooperate with law enforcement [@Desmond2016; @Tyler2014]. Legitimacy studies have largely focused on police violence or police street stops, but new evidence related to fines and fees has recently emerged. 
In a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government more broadly [@CarpenterII2019].

Although the conceptual framework for police legitimacy has been fruitfully critiqued --- Monica @Bell2017 points to legal estrangement and structural exclusion in order to shift the theoretical focus from perceptions of unfairness to substantively unjust practices --- the empirical literature on legitimacy is useful to demonstrate how police practices can alienate those subjected to them.  The alienating effect of criminal legal exposure has also been tied to institutional avoidance [see, for instance, @Brayne2014]. .

@@

Figures \ref{fig:to} and \ref{fig:to-gap} make clear that higher fees and fines collections are associated with lower turnout *and* a lower turnout gap. Figure \ref{fig:to} plots the simple bivariate relationship between turnout among registered voters in 2018 and fees and fines collection, while Figure \ref{fig:to-gap} shows the bivariate relationship between the 2018 white-Black turnout gap and fines collections. The turnout gap is calculated by dividing the number of ballots cast by each racial group according to L2 by the estimated 2018 citizen voting age population (CVAP) for that group from the Census Bureau to account for possible registration differences between groups.

Figures \ref{fig:to} and \ref{fig:to-gap} cannot demonstrate a causal relationship. To investigate whether there is such a relationship, we employ two-way fixed effect models. In these models, each municipality is observed twice: their first observation includes their (logged + 1) fees and fines per capita from the 2012 COG, their turnout and turnout gap in 2014, and their sociodemographic characteristics from the ACS 5-year estimates from 2012. The second observation includes their (logged + 1) fees and fines from the 2017 COG, their 2018 turnout (gap), and their 2018 5-year ACS demographics. In each case, turnout is measured only among the individuals who were registered in a given municipality in both 2014 and 2018 to control for changes in registration rates, and in Model 2 the turnout gap is calculated using CVAP in each year. Table \ref{tab:tab1} presents the results of these models. Table \ref{tab:tab1} demonstrates that fees and fines collections likely have a causal effect on voter turnout and the turnout gap. A 10 percent increase in collections is associated with a roughly 3.3 percentage point decrease in turnout, and a 1.8 percentage point decrease in the racial turnout gap.

Our preliminary results with respect to turnout are not particularly surprising: prior literature led us to expect that, as municipalities increased their fees and fines, voters would become alienated from their government and opt out of democratic participation. Nevertheless, these are substantive impacts.

That increased collections reduce the racial turnout gap is surprising, and the opposite of what we expected to find. This could reflect racially disparate policing in cities with low fee collection. It is possible that as fees and fines collections increase a larger share of the population --- and, thus, more white voters --- may have a negative interaction with a police officer, thereby reducing racial disparities in fines and fees and, consequently, discrepancies in the racial turnout gap.

Our full study will include a more narrow analysis of turnout in jurisdictions that dramatically increased or decreased ticketing over a comparatively short period of time. For instance, a Florida Times-Union investigation revealed that police in four counties disproportionately issued tickets to Black pedestrians [@Sanders2017]. In Tampa, police issued thousands of tickets to Black cyclists between 2012 and 2015 --- after journalists reported on the problem, the city began to issue fewer than 100 citations each year as of 2018 [@Zayas2015; @Frago2019]. Systematically conducting such an analysis would likely require collecting and organizing new data, as city-level police ticketing data is inconsistent and not always public information.

\newpage
### Bibliography {-}
<div id="refs"></div>

\newpage
\pagenumbering{gobble}
\pagenumbering{arabic}
## Appendix A {-}

```{r, figures-side, fig.show="hold", out.height="40%", echo = FALSE, message = F, warning = F, fig.cap = "\\label{fig:to}Dollars per Resident and 2018 Turnout", fig.pos = "H", fig.align = "center"}
p1 <- readRDS("./temp/simple_scat.rds")
print(p1)
```

```{r, fig.show="hold", out.height="40%", echo = FALSE, message = F, warning = F, fig.cap = "\\label{fig:to-gap}Dollars per Resident and 2018 Turnout Gap", fig.pos = "H", fig.align = "center"}
p1 <- readRDS("./temp/simple_scat_gap_bw.rds")
print(p1)
```

@@

### 2021-01-27 markdown/fees_fines_to.tex
keep writing

Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities' alienation from government. American cities' reliance on fines and fees revenue increased significantly following the 2008 recession---as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services (Singla, Kirschner, and Stone \protect\hyperlink{ref-Singla2020}{2020}; Mughan \protect\hyperlink{ref-Mughan2020}{2020}; Kirk, Fernandes, and Friedman \protect\hyperlink{ref-Kirk2020}{2020}; Martin \protect\hyperlink{ref-Martin2018}{2018}). Although a body of literature developed over the past decade indicates that criminalization chills political participation, no work has directly investigated the relationship between fines and fees revenue collection and voter turnout. This project intends to fill that gap by testing whether fines and fees at the municipal level influence voter turnout.

@@

Recent work from scholars in sociology and political science, however, indicates that many more voters are also \emph{indirectly} disenfranchised due to over-incarceration and the politically chilling effects of the carceral state. Policing and incarceration shape political socialization: personal contact with police or incarceration is associated with a reduced likelihood of political participation, and that alienating effect extends even to people who have incarcerated family members or who simply reside in affected communities (Lee, Porter, and Comfort \protect\hyperlink{ref-Lee2014}{2014}; Weaver and Lerman \protect\hyperlink{ref-Weaver2010}{2010}; Morris \protect\hyperlink{ref-Morris2020}{2020}). This relationship is complicated, however. In New York City, concentrated stop-and-frisk activity was associated with \emph{reduced} turnout in Congressional elections, but \emph{increased} turnout in the 2008 presidential election as well as the local mayoral election in 2013 (Laniyonu \protect\hyperlink{ref-Laniyonu2019}{2019}). It may also be the case that proximal contact differs from personal contact with the criminal legal system---whereas direct experience with criminalization (and incarceration in particular) reduces the likelihood of voting, proximal or indirect experience produces more mixed results. Hannah Walker suggests that police contact that does not lead to a criminal conviction may even mobilize voters---but her survey questions specifically excluded ``minor traffic stops,'' a primary site of police ticketing (Walker \protect\hyperlink{ref-Walker2014}{2014}).

@@

Public perceptions of abusive police practices, such as high-profile incidents of police violence or racially discriminatory street stops, can reduce willingness to report crimes or cooperate with law enforcement {[}Desmond, Papachristos, and Kirk (\protect\hyperlink{ref-Desmond2016}{2016}); Tyler, Fagan, and Geller (\protect\hyperlink{ref-Tyler2014}{2014})). Legitimacy studies have largely focused on police violence or police street stops, but new evidence related to fines and fees has recently emerged.
In a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government more broadly (Carpenter II, Sweetland, and McDonald \protect\hyperlink{ref-CarpenterII2019}{2019}).

Although the conceptual framework for police legitimacy has been fruitfully critiqued---Monica Bell (\protect\hyperlink{ref-Bell2017}{2017}) points to legal estrangement and structural exclusion in order to shift the theoretical focus from perceptions of unfairness to substantively unjust practices---the empirical literature on legitimacy is useful to demonstrate how police practices can alienate those subjected to them. The alienating effect of criminal legal exposure has also been tied to institutional avoidance (see, for instance, Brayne \protect\hyperlink{ref-Brayne2014}{2014}). .

@@

Figure \ref{fig:marg1} makes clear that higher fees and fines collections lead to lower turnout. The left-hand panel shows the simple bivariate relationship between turnout among registered voters in 2018 and fees and fines collection. The right-hand panel shows the bivariate relationship between the 2018 white-Black turnout gap and fines collections. The turnout gap is calculated by dividing the number of ballots cast by each racial group according to L2 by the estimated 2018 citizen voting age population (CVAP) from the Census Bureau to account for possible registration differences between groups.

\begin{figure}[H]
\includegraphics[width=0.5\linewidth]{fees_fines_to_files/figure-latex/figures-side-1} \includegraphics[width=0.5\linewidth]{fees_fines_to_files/figure-latex/figures-side-2} \caption{\label{fig:marg1}Dollars per Resident and 2018 Turnout}\label{fig:figures-side}
\end{figure}

Although Figure \ref{fig:marg1} shows that there is a relationship between collections and turnout and the turnout gap, the simple scatter plots cannot demonstrate a causal relationship. To investigate whether there is such a relationship, we employ two-way fixed effect models. In these models, each municipality is observed twice: their first observation includes their (logged + 1) fees and fines per capita from the 2012 COG, their turnout and turnout gap in 2014, and their sociodemographic characteristics from the ACS 5-year estimates from 2012. The second observation includes their (logged + 1) fees and fines from the 2017 COG, their 2018 turnout (gap), and their 2018 5-year ACS demographics. In each case, turnout is measured only among the individuals who were registered in a given municipality in both 2014 and 2018 to control for changes in registration rates, and in Model 2 the turnout gap is calculated using CVAP. Table \ref{tab:tab1} presents the results of these models.

@@

The significant negative association in our analysis provides some support for our first hypothesis: though our preliminary analyses cannot establish causality, they are consistent with a causal story that links fines and fees practices with lower political participation among those who are subjected to them. On the other hand, officials in municipalities with lower turnout may feel more free to rely on fees and fines for revenue collection because they have less fear of electoral repercussions. Our full study will explore these causal relationships directly by supplementing our initial analysis with an analysis of voter turnout and revenue reliance change over time.

That the racial turnout gap is smaller in cities with more fees and fines is surprising, and the opposite of what we expected to find. This could reflect racially disparate policing in cities with low fee collection. It is possible that cities with \emph{low} fees and fines collections disproportionately penalize nonwhite residents; as fees and fines collections increase, however, a larger share of the population --- and, thus, more white voters --- may have a negative interaction with a police officer, thereby \emph{reducing} racial disparities and consequently discrepancies in the racial turnout gap.

Our full study will include a more narrow analysis of turnout in jurisdictions that dramatically increased or decreased ticketing over a comparatively short period of time. For instance, a Florida Times-Union investigation revealed that police in four counties disproportionately issued tickets to Black pedestrians (Sanders and Conarck \protect\hyperlink{ref-Sanders2017}{2017}). In Tampa, police issued thousands of tickets to Black cyclists between 2012 and 2015---after journalists reported on the problem, the city began to issue fewer than 100 citations each year as of 2018 (Zayas \protect\hyperlink{ref-Zayas2015}{2015}; Frago \protect\hyperlink{ref-Frago2019}{2019}). Systematically conducting such an analysis would likely require collecting and organizing new data, as city-level police ticketing data is inconsistent and not always public information.

@@

>>>>

Fines and fees are increasingly recognized as a form of racist revenue extraction connected to marginalized communities' alienation from government. American cities' reliance on fines and fees revenue increased significantly following the 2008 recession --- as local tax revenues dropped and tax increases became less politically viable, jurisdictions increased the amounts of fines and fees and imposed them more frequently in order to fund government services (Singla, Kirschner, and Stone \protect\hyperlink{ref-Singla2020}{2020}; Mughan \protect\hyperlink{ref-Mughan2020}{2020}; Kirk, Fernandes, and Friedman \protect\hyperlink{ref-Kirk2020}{2020}; Martin \protect\hyperlink{ref-Martin2018}{2018}). Although a body of literature developed over the past decade indicates that criminalization chills political participation, no work has directly investigated the relationship between fines and fees revenue collection and voter turnout. This project intends to fill that gap by testing whether fines and fees at the municipal level influence voter turnout.

@@

Recent work from scholars in sociology and political science, however, indicates that many more voters are also \emph{indirectly} disenfranchised due to over-incarceration and the politically chilling effects of the carceral state. Policing and incarceration shape political socialization: personal contact with police or incarceration is associated with a reduced likelihood of political participation, and that alienating effect extends even to people who have incarcerated family members or who simply reside in affected communities (Lee, Porter, and Comfort \protect\hyperlink{ref-Lee2014}{2014}; Weaver and Lerman \protect\hyperlink{ref-Weaver2010}{2010}; Morris \protect\hyperlink{ref-Morris2020}{2020}). This relationship is complicated, however. In New York City, concentrated stop-and-frisk activity was associated with \emph{reduced} turnout in Congressional elections, but \emph{increased} turnout in the 2008 presidential election as well as the local mayoral election in 2013 (Laniyonu \protect\hyperlink{ref-Laniyonu2019}{2019}). It may also be the case that proximal contact differs from personal contact with the criminal legal system --- whereas direct experience with criminalization (and incarceration in particular) reduces the likelihood of voting, proximal or indirect experience produces more mixed results. Hannah Walker suggests that police contact that does not lead to a criminal conviction may even mobilize voters --- but her survey questions specifically excluded ``minor traffic stops,'' a primary site of police ticketing (Walker \protect\hyperlink{ref-Walker2014}{2014}).

@@

Public perceptions of abusive police practices, such as high-profile incidents of police violence or racially discriminatory street stops, can reduce willingness to report crimes or cooperate with law enforcement (Desmond, Papachristos, and Kirk \protect\hyperlink{ref-Desmond2016}{2016}; Tyler, Fagan, and Geller \protect\hyperlink{ref-Tyler2014}{2014}). Legitimacy studies have largely focused on police violence or police street stops, but new evidence related to fines and fees has recently emerged.
In a survey of residents in three Georgia cities that rely heavily on fines and fees revenue, residents who were ticketed reported lower levels of trust in police and government more broadly (Carpenter II, Sweetland, and McDonald \protect\hyperlink{ref-CarpenterII2019}{2019}).

Although the conceptual framework for police legitimacy has been fruitfully critiqued --- Monica Bell (\protect\hyperlink{ref-Bell2017}{2017}) points to legal estrangement and structural exclusion in order to shift the theoretical focus from perceptions of unfairness to substantively unjust practices --- the empirical literature on legitimacy is useful to demonstrate how police practices can alienate those subjected to them. The alienating effect of criminal legal exposure has also been tied to institutional avoidance (see, for instance, Brayne \protect\hyperlink{ref-Brayne2014}{2014}). .

@@

Figures \ref{fig:to} and \ref{fig:to-gap} make clear that higher fees and fines collections are associated with lower turnout \emph{and} a lower turnout gap. Figure \ref{fig:to} plots the simple bivariate relationship between turnout among registered voters in 2018 and fees and fines collection, while Figure \ref{fig:to-gap} shows the bivariate relationship between the 2018 white-Black turnout gap and fines collections. The turnout gap is calculated by dividing the number of ballots cast by each racial group according to L2 by the estimated 2018 citizen voting age population (CVAP) for that group from the Census Bureau to account for possible registration differences between groups.

Figures \ref{fig:to} and \ref{fig:to-gap} cannot demonstrate a causal relationship. To investigate whether there is such a relationship, we employ two-way fixed effect models. In these models, each municipality is observed twice: their first observation includes their (logged + 1) fees and fines per capita from the 2012 COG, their turnout and turnout gap in 2014, and their sociodemographic characteristics from the ACS 5-year estimates from 2012. The second observation includes their (logged + 1) fees and fines from the 2017 COG, their 2018 turnout (gap), and their 2018 5-year ACS demographics. In each case, turnout is measured only among the individuals who were registered in a given municipality in both 2014 and 2018 to control for changes in registration rates, and in Model 2 the turnout gap is calculated using CVAP in each year. Table \ref{tab:tab1} presents the results of these models. Table \ref{tab:tab1} demonstrates that fees and fines collections likely have a causal effect on voter turnout and the turnout gap. A 10 percent increase in collections is associated with a roughly 3.3 percentage point decrease in turnout, and a 1.8 percentage point decrease in the racial turnout gap.

@@

Our preliminary results with respect to turnout are not particularly surprising: prior literature led us to expect that, as municipalities increased their fees and fines, voters would become alienated from their government and opt out of democratic participation. Nevertheless, these are substantive impacts.

That increased collections reduce the racial turnout gap is surprising, and the opposite of what we expected to find. This could reflect racially disparate policing in cities with low fee collection. It is possible that as fees and fines collections increase a larger share of the population --- and, thus, more white voters --- may have a negative interaction with a police officer, thereby reducing racial disparities in fines and fees and, consequently, discrepancies in the racial turnout gap.

Our full study will include a more narrow analysis of turnout in jurisdictions that dramatically increased or decreased ticketing over a comparatively short period of time. For instance, a Florida Times-Union investigation revealed that police in four counties disproportionately issued tickets to Black pedestrians (Sanders and Conarck \protect\hyperlink{ref-Sanders2017}{2017}). In Tampa, police issued thousands of tickets to Black cyclists between 2012 and 2015 --- after journalists reported on the problem, the city began to issue fewer than 100 citations each year as of 2018 (Zayas \protect\hyperlink{ref-Zayas2015}{2015}; Frago \protect\hyperlink{ref-Frago2019}{2019}). Systematically conducting such an analysis would likely require collecting and organizing new data, as city-level police ticketing data is inconsistent and not always public information.

@@

\newpage
\pagenumbering{gobble}
\pagenumbering{arabic}

\hypertarget{appendix-a}{%
\subsection*{Appendix A}\label{appendix-a}}
\addcontentsline{toc}{subsection}{Appendix A}

\begin{figure}[H]

{\centering \includegraphics[height=0.4\textheight]{fees_fines_to_files/figure-latex/figures-side-1}

}

\caption{\label{fig:to}Dollars per Resident and 2018 Turnout}\label{fig:figures-side}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[height=0.4\textheight]{fees_fines_to_files/figure-latex/unnamed-chunk-1-1}

}

\caption{\label{fig:to-gap}Dollars per Resident and 2018 Turnout Gap}\label{fig:unnamed-chunk-1}
\end{figure}
